Working Principles of Proof Assistants and Formalization of some proofs in Agda

### 2025-08-04 Mainpaper/paper.tex
minor fixes in unicode notation and declaration
cover page , ack page and minor changes

% ======== Packages =========
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{geometry}
\usepackage{bussproofs}
\usepackage{braket}
\geometry{a4paper, margin=1in}
\usepackage{titlesec}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, positioning}
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{1em}{}

\title{Working Principles of Proof Assistants and Formalization of some proofs in Agda}
\author{Bishesh Bohora, Supreme Chaudhary, Ashwot Acharya \\
\small Kathmandu University 
\small \texttt{}
}
%mention supervisor
\date{\today}

@@

\maketitle

\clearpage
\section*{}
\addcontentsline{toc}{section}{\textbf{ABSTRACT}}

@@

prop23 : (forall x → A x → B x) → (s : X) → A s → Sigma X B
prop23 allImp s aS = s , allImp s aS
--Replace sigma with greek alphabet while loading.

prop24 : forall {A B : Set} -> A -> B -> A
prop24 a b = a
\end{verbatim}

>>>>

% ======== Packages =========
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{geometry}
\usepackage{bussproofs}
\usepackage{braket}
\geometry{a4paper, margin=1in}
\usepackage{titlesec}
\usepackage{newunicodechar}
\usepackage{tikz}
\DeclareUnicodeCharacter{2200}{\ensuremath{\forall}}    % ∀
\DeclareUnicodeCharacter{2113}{\ensuremath{\ell}}       % ℓ
\DeclareUnicodeCharacter{2192}{\ensuremath{\rightarrow}}% →
\DeclareUnicodeCharacter{00D7}{\ensuremath{\times}}     % ×
\DeclareUnicodeCharacter{228E}{\ensuremath{\uplus}}   % ⊎
\DeclareUnicodeCharacter{22A5}{\ensuremath{\bot}}       % ⊥
\DeclareUnicodeCharacter{00AC}{\ensuremath{\neg}}       % ¬
\DeclareUnicodeCharacter{2081}{\textsubscript{1}}       % ₁
\DeclareUnicodeCharacter{2082}{\textsubscript{2}}       % ₂
\DeclareUnicodeCharacter{03BB}{\ensuremath{\lambda}}    % λ
\DeclareUnicodeCharacter{03A3}{\ensuremath{\Sigma}}   % Σ
\geometry{
  left=1.2in,
  right=1.2in,
  top=1.1in,
  bottom=1.1in
}
\usetikzlibrary{arrows.meta, positioning}
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{1em}{}

\title{Working Principles of Proof Assistants and Formalization of some proofs in Agda}
\author{Bishesh Bohora, Supreme Chaudhary, Ashwot Acharya \\
\small Kathmandu University 
\small \texttt{}
}
\date{\today}

@@

\begin{titlepage}
    \begin{center}
        % Title
        \Large\bfseries
        Working Principles of Proof Assistants and Formalization of some proofs in Agda\\[2cm]

        \normalsize
        SECOND YEAR PROJECT REPORT\\[2ex]

        \small
        SUBMITTED IN PARTIAL FULFILLMENT OF THE REQUIREMENTS FOR\\
        THE DEGREE OF MSC. IN COMPUTATIONAL MATHEMATICS\\[2cm]

        \normalsize
        BY\\[2ex]
        \textbf{Ashwot Acharya, Bishesh Bohora, Supreme Chaudhary}\\[2cm]

        \includegraphics[width=4cm]{logo.png}\\[2cm]
        % Replace with your logo file. Place 'ku_logo.png' in the same folder!

        DEPARTMENT OF MATHEMATICS\\
        KATHMANDU UNIVERSITY\\
        DHULIKHEL, NEPAL\\[2ex]

        \vfill
    \end{center}
\end{titlepage}

\thispagestyle{empty}

\begin{center}
    \textbf{\LARGE CERTIFICATION}
\end{center}

\vspace{1em}

This project entitled ``\textbf{Working Principles of Proof Assistants and Formalization of some proofs in Agda}'' is carried out under our supervision for the specified entire period satisfactorily and is hereby certified as a work done by the following students:
\begin{enumerate}
    \item Ashwot Acharya
    \item Bishesh Bohora 
    \item Supreme Chaudhary
\end{enumerate}
in partial fulfillment of the requirements for the degree of B.Sc. in Computational Mathematics, Department of Mathematics, Kathmandu University, Dhulikhel, Nepal.

\vspace{3em}

\noindent
\begin{minipage}{0.45\textwidth}
\rule{6cm}{0.5pt}\\
\textbf{M.r K.B Manandhar }\\
Assistant Professor\\
Department of Mathematics,\\
School of Science\\ Kathmandu University,\\
Dhulikhel, Kavre, Nepal\\
Date: August, 2025

\end{minipage}

\vspace{2.5em}

\noindent
\\ \\ 
\textbf{APPROVED BY:}\\
I hereby declare that the candidate qualifies to submit this report of \textbf{Working Principles of Proof Assistants and Formalization of some proofs in Agda} to the Department of Mathematics.
\\
\vspace{1.7em}
\\
\noindent
\rule{6cm}{0.5pt}\\ \\
\textbf{Head of Department }\\
Department of Mathematics\\
School of Science\\
Kathmandu University\\
Date: August, 2025

\vspace{2em}

\begin{center}
   {\small ii}
\end{center}
\clearpage

\addcontentsline{toc}{section}{\textbf{ABSTRACT}}  
\clearpage

\begin{center}
    \textbf{\LARGE ACKNOWLEDGMENTS}
\end{center}
    First and foremost, we would like to thank our supervisor Mr K.B Manandhar sir for guiding us through this research project.
Their feedback and suggestions helped us overcome numerous challenges and shaped
our understanding of the subject matter.

@@

prop23 : (∀ x → A x → B x) → (s : X) → A s → Σ X B
prop23 allImp s aS = s , allImp s aS

prop24 : ∀ {A B : Set} -> A -> B -> A
prop24 a b = a
\end{verbatim}
